PODD Ontology Driven Database

### 2012-03-09 epncanberra2012/Podd-20120313.tex
make a blank slide with a bigger version of the podd ontology which should scale with screen size
fix second to last slide
add architecture diagram as svg and png

@@

\begin{frame}
\frametitle{Design}

\begin{frame}[t]
\frametitle{Phenomics ontology for PODD}
\invisible

\begin{center}
 \includegraphics[scale=0.36,keepaspectratio=true]{./podd_ont.pdf}
 % podd_ont.pdf: 720x540 pixel, 72dpi, 25.40x19.05 cm, bb=0 0 720 540
\end{center}
\end{frame}

@@

@@

\begin{frame}

\url{http://github.com/podd}

peter.ansell@uq.edu.au

@@

Open source code can be found online at:

@@

My email is: peter.ansell@uq.edu.au

>>>>

\begin{itemize}
 \item PODD implemented between 2009 and 2011
 \item Design by Yuan Fang Li and Gavin Kennedy
\end{itemize}

@@

% PODD Design/Architecture as a blank slide
\bgroup
\usebackgroundtemplate{\includegraphics[
width=\paperwidth,
height=\paperheight,
keepaspectratio=true
]{podd_arch.png}}
\begin{frame}[plain]{}
\end{frame}
\egroup

% PODD Phenomics Ontology as a blank slide
\bgroup
\usebackgroundtemplate{\includegraphics[
width=\paperwidth,
height=\paperheight,
keepaspectratio=true
]{podd_ont.png}}
\begin{frame}[plain]{}
\end{frame}
\egroup

@@

Good:

\begin{enumerate}
 \item Flexible : Simultaneously support different experiments
 \item Adaptable : Additions and changes to schema ontologies
\end{enumerate}

Bad:

\begin{enumerate}
 \item Current implementation does not scale
 \item Object oriented, pulling document into memory
\end{enumerate}

@@

@@

\begin{center}
Open source code can be found online at:

@@

\vskip 12pt

My email is: peter.ansell@uq.edu.au
\end{center}
\end{frame}
